\section{Introduction}

Other tools used for metabolic network curation and visualization (maybe I can make a table).
Curation: 

Semi-automated Curation of Metabolic Models via Flux Balance Analysis: A Case Study with Mycoplasma gallisepticum <- more than a tool is an algorithm.

Use of a global metabolic network to curate organismal metabolic networks <- again an algorithm?

Enhancing genetic algorithm-based genome-scale metabolic network curation efficiency <- algorithm

RAVEN -> tool to create and curate metabolic networks.

Transparency in metabolic network reconstruction enables scalable biological discovery -> explains a bit about curation in metabolic models

http://biocuration.org/ <- The ISB is a non profit organisation for biocurators (It is more general for all kind of biological data)

Network Thermodynamic Curation of Human and Yeast Genome-Scale Metabolic Models <- algorithm to curate the reaction directions using thermodynamics.

Fifteen years of large scale metabolic modeling of yeast: Developments and impacts <- the Figure 1 shows the basic steps for the model reconstruction. Explain which of these steps can be improved wiht AntND

The SuBliMinaL Toolbox: automating steps in the reconstruction of metabolic networks. <- Tool for the creation of metabolic models. It can be consider also a curation tool because it contains many modules.

PathwayBooster: a tool to support the curation of metabolic pathways <- and actual tool for the curation. It has more tools related to the gene annotation. It works on/with the suBliMinaL tool.

Reconstruction and curation of a metabolic model can't be considered two independent steps. They are overlapping in many cases in the tools. We use CoReCo as a reconstruction tool which already provides the gene annotations steps. 
One important asset of AntND is the possible connection to our database. Is it possible to include the database curation?

